---
output:
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 2
---

# The use of stereo-video monitoring and physiological trials to estimate metabolic demands of reef fishes in the wild

This repository contains the code and data to reproduce all tables and figures presented in Schiettekatte, Conte et al. "The use of stereo-video monitoring and physiological trials to estimate metabolic demands of reef fishes in the wild".


## Instructions
All analyses for the current project were done in R, using the drake pipeline [drake](https://github.com/ropensci/drake). You can use drake to compile all models, figures, and tables.
To do so, first install `drake` from CRAN: 
```{r, eval=FALSE}
install.packages("drake")
```
Next you need to open an R session with working directory set to the root of the project.    

We use a number of packages, listed in `r/packages.R`. If needed, missing packages should first be installed. 

Then, to generate all figures, analyses, and tables, simply run:

```{r, eval = FALSE}
drake::r_make()
```

All output will be automatically rendered inside the folder called output. 

## Details
The elements of this project include: 

1) data: this folder includes all the raw data necessary to run the script.
2) output: this folder includes all outputs from the R-script, including figures and the manuscript in docx.
3) text: this folder includes the raw manuscript, and cover letter.
4) R: this folder contains three .R files, `packages.R`, `functions.R`, and `plan.R`.     
`packages.R` contains all packages needed, `functions.R` contains all functions to reproduce the analyses, and `plan.R` provides the code that binds each step of the workflow.

## Datasets

1. data_fulton_2007 = data from Fulton et al. (2007) containing maximum swimming speeds of fishes.

2. data_respirometry = Respirometry: these data are derived from intermittent respirometry, performed in the lab at CRIOBE. Each row is an individual fish and its associated metadata. SMR = standard metabolic rate in mg O2 per h. MaxMR = maximum metabolic rate in mg O2 per h. MeanTemp...C. = temperature in ºCelsius. Weight..kg. = mass in g.

3. video_swimming_speeds = Measurements of size and swimming speed of our seven model species, obtained through video analysis using the software VidSync. 

4. data_uvc_moo_2016_fsp = Underwater visual census data, snapshot of a long-term monitoring program, kindly shared by CRIOBE, Moorea. 


This paper was produced using the following software and associated packages:

```{r, echo=FALSE}
devtools::session_info()
```


All code written by Francesca Conte and Nina M. D. Schiettekatte (nina.schiettekatte@gmail.com). Please contact us for any issue or question. 
